Push-Pull Signal-Function Functional Reactive Programming

### 2012-11-30 Docs/IFL2012/introduction.tex
Partial pass on intro

An FRP system provides a means of manipulating {\em signals} and
{\em events}. Signals are often referred to as {\em behaviors} in FRP literature,
but the definition is the same.  Semantically, a signal or behavior is a
function from time to a value. An event is a ordered sequence of discrete
occurrences, carrying both values and timestamps. In our example, inputs from
the barometers, anemometers, and rain gauges would be abstracted as signals. The
information carried by the signal would be the measurement made by the
instrument, perhaps tagged with the instrument's location. The input from the
lighting detector would be an event, whose occurrences would each carry the
location and intensity of a lightning strike.

One key distinction in FRP systems concerns how signals and events are
evaluated. There are two possibilities. Pull-based evaluation uses repeated and
frequent updates in a loop to check for updated values (similar to busy waiting
in concurrency, except that for signals, there should be no waiting). Push-based
evaluation blocks or waits to be notified about an updated value, similar to
notification in concurrency. Pull-based evaluation is appropriate for signals,
which approximate continuous values and should have a value available whenever
they are sampled. Push-based evaluation is appropriate for events, which must be
reacted to quickly without consuming unnecessary resources to wait. Turning
again to our example: it is appropriate for our system to repeatedly query the
pressure, wind speed, and rain levels. The system should respond quickly to
lightning strikes, but should not use resources in repeatedly sampling for the
occurrence, or not, of a lightning strike. The system should instead be notified
when a strike has occurred.

>>>>

An FRP system provides a means of manipulating {\em signals} and
{\em events}. Signals are often referred to as {\em behaviors} in earlier FRP literature,
but the definition is the same.  Semantically, a signal or behavior is a
function from time to a value. An event is a ordered sequence of discrete
occurrences, \textred{carrying both values and timestamps}. In our example, inputs from
the barometers, anemometers, and rain gauges would be signals. The
information carried by the signal would be the measurement made by the
instrument, perhaps tagged with the instrument's location. The input from the
lighting detector would be an event, whose occurrences would each carry the
location and intensity of a lightning strike.

One key distinction in FRP systems concerns how signals and events are
evaluated. There are two possibilities. Pull-based evaluation uses repeated and
frequent updates in a loop to check for updated values (polling).
% (similar to busy waiting in concurrency, except that for signals, there should be no waiting). 
\rn{``In concurrency'' seems awkward.  Maybe ``in concurrent
  programming'', or just nix.  What do you think of this alternative?}
Push-based
evaluation blocks or waits to be notified about an updated value (blocking).
% , similar to notification in concurrency. 
Pull-based evaluation is appropriate for signals,
which approximate continuous values and should have a value available whenever
they are sampled. Push-based evaluation is appropriate for events, which must be
reacted to quickly without consuming unnecessary resources to wait. Turning
again to our example: it is appropriate for our system to repeatedly query the
pressure, wind speed, and rain levels \new{to update the real-time model}. The system should respond quickly to
lightning strikes, but should not use resources in repeatedly sampling for the
occurrence (or not) of a lightning strike.  The system should instead be notified
when a strike has occurred.  \new{Further, this notification should {\em not} result in 
recomputeing all signals upon each strike event.}
